Donor Responses to Civil Society Repression

### 2024-11-05 README.qmd
Add abstract

yaml_metadata <- rmarkdown::yaml_front_matter("index.qmd")
title <- yaml_metadata$title
# abstract <- yaml_metadata$abstract
abstract <- "Given the increase in administrative and legal repression of civil society, how have their donors responded? How do these responses differ across foreign government and private donors? How have local philanthropists and NGOs adapted and responded to such repression? What challenges do civil society groups continue to face despite these responses?"
```

>>>>

yaml_metadata <- rmarkdown::yaml_front_matter("index.qmd")
title <- yaml_metadata$title
abstract <- yaml_metadata$abstract
```

### 2024-11-05 index.qmd
Add abstract

>>>>

abstract: |
  This chapter examines donor responses to the global crackdown on civil society, where governments use legal measures to repress NGOs. Donors, including bilateral and multilateral agencies, respond variably; bilateral aid often decreases following anti-NGO laws, while multilateral aid remains stable. Private donors' responses depend on factors like social trust and NGO transparency. NGOs adapt by diversifying funding, forming affiliates, or shifting to community-based support. As the space for civil society continues to shrink, coordinated international efforts are essential to counteract these repressive trends and uphold civil society's role in democratic governance.
